---
title: "Foofactors"
author: "Edited by Jiahui Tang, created by Jenny Bryan"
output:
  rmarkdown::html_vignette:
    toc: true
    keep_md: true
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This file works based on Jenny Bryan's coding, and I added some functions after it.

Factors are a very useful type of variable in R, but they can also drive you nuts. Especially the "stealth factor" that you think of as character.

Can we soften some of their sharp edges?

Binding two factors via `fbind()`:

```{r}
library(foofactors)
a <- factor(c("character", "hits", "your", "eyeballs"))
b <- factor(c("but", "integer", "where it", "counts"))
```

Simply catenating two factors leads to a result that most don't expect.

```{r}
c(a, b)
```

The `fbind()` function glues two factors together and returns factor.

```{r}
fbind(a, b)
```

Often we want a table of frequencies for the levels of a factor. The base `table()` function returns an object of class `table`, which can be inconvenient for downstream work.  Processing with `as.data.frame()` can be helpful but it's a bit clunky.

```{r}
set.seed(1234)
x <- factor(sample(letters[1:5], size = 100, replace = TRUE))
table(x)
as.data.frame(table(x))
```

The `freq_out()` function returns a frequency table as a well-named `tbl_df`:

```{r}
freq_out(x)
```

Above codes are based on Jenny's notes. Here I created more functions about dealing with factor.

Most of time we often want to figure out if the factors should be character. We can use`detect_factors`to check if some of the element of the factor are not unique. Otherwise, if all of the elements are unique, you probably should use it as character.

```{r}
a <- factor(c("a","b","c")) ##Should be character
b <- factor(c("a","b","b")) ##Should be factor

detect_factors(a)
detect_factors(b)
```

